Forecast of the 2024 Presidential Election through the Lens of Turbulent Swing States

### 2024-11-04 paper/paper.qmd
Update paper.

---
title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Swing States"
subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 4 of 7 Swing States"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election. Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{pdfpages}
---

@@

@@

# Results
The analysis of polling data across key swing states for the 2024 U.S. Presidential Election reveals insights into the levels of support for candidates Donald Trump and Kamala Harris. The findings are presented through three primary visualizations: the average polling percentage by state, the distribution of polling percentages, and the difference in average polling percentage between the two candidates.

>>>>

---
title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Swing States"
subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 4 of 7 Swing States"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election. Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

In the **Data** section (see [Section 2](#sec-data)), we describe the sources and processing steps involved in preparing our dataset. Following that, the **Model** section (see [Section 3](#sec-model)) outlines the statistical model used to analyze the data and make predictions.

The **Results** section (see [Section 4](#sec-result)) provides an overview of the model's forecasts and key findings, while the **Discussion** (see [Section 5](#sec-discussion)) interprets these results and considers broader implications. For additional technical information, including detailed model specifications, refer to the **Model Details** subsection (see [Section 5.1](#sec-model-details)).

@@

# Results {#sec-result}
The analysis of polling data across key swing states for the 2024 U.S. Presidential Election reveals insights into the levels of support for candidates Donald Trump and Kamala Harris. The findings are presented through three primary visualizations: the average polling percentage by state, the distribution of polling percentages, and the difference in average polling percentage between the two candidates.
